---
title: "MATH 3070 Lab Project 3"
author: "Kanishka Ragula"
date: "September 1, 2016"
output:
  html_document:
    toc: TRUE
---

*Remember: I expect to see commentary either in the text, in the code with comments created using `#`, or (preferably) both! **Failing to do so may result in lost points!***

## Problem 1
*The `faithful` (Package **datasets** is built in Base R) dataset records the waiting time between eruptions and the duration of the eruption for the Old Faithful geyser in Yellowstone National Park. Find the mean waiting time, median waiting time, longest waiting time and shortest waiting time in minutes.*

```{r}
library(UsingR)
#Prints mean
mean(faithful$waiting)
#Prints median
median(faithful$waiting)
#Prints max
max(faithful$waiting)
#Prints min
min(faithful$waiting)
```

## Problem 2 (Verzani problem 2.34)
*The data set `DDT` (**MASS**) contains independent measurements of the pesticide DDT on kale. Make a histogram and a boxplot of the data. From these, estimate the mean and standard deviation. Check your answers with the appropriate functions.*

```{r}
#Creates a Histogram of DDT
hist(DDT)

#Creates a Boxplot for DDT
boxplot(DDT)

#Calculates mean of DDT
mean(DDT)

#Calculates standard Deviation of DDT
sd(DDT)
```

## Problem 3 (Verzani problem 2.32 modified)
*Write a function 'density_compare()' that fits a density estimate to a given data set and plots that estimate along with the appropriate histogram of the given data set. Try your function with the data set `pi2000` (**UsingR**). Why might you want to add an argument like `breaks = 0:10-.5` to `hist()`? (Hint: read the documentation of `hist()` to see what setting this argument does). Feel free to add other parameters to your plot methods to see how they can be changed.*

```{r}
#Declare function and parameters
density_compare = function(x){
  
  #Create the Histogram of x
  hist(x, 
       main = "Distribution of Desired Dataset",
       #Color Gray
       col = "gray",
       #Turn off frequency so it fits on density
       freq = FALSE,
       
       #Break makes it so the breaks show every number, not just the groups of two.
       breaks = 0:10 - .5)
  #Plots density curve
  lines(density(x))
}
density_compare(pi2000)
```

## BONUS (Verzani problem 2.25)
*Write a function `isprime()` that checks if a number $x$ is prime by dividing $x$ by all the values in $2, ..., x - 1$ then checking to see if there is a remainder of 0. The expression `a %% b` returns the remainder of `a` divided by `b`.*

```{r}
# Method and parameters 
isprime = function(x){
  #Set first value to be divided by for test
  varInc = 2
  #Variabe that stores whether or not a prime
  #Defaults to true
  priminess = TRUE;
  #While loop which increments varInc until varInc = x-1
  while((varInc < x) && priminess){
    #Calculate Remainder
    remainder = x%%varInc
    if(remainder == 0){
      #If remainder is zero, it isn't prime and sets isPrime to false
      priminess = FALSE;
    }
    #Increment
    varInc = varInc + 1
  }
  #Print results
  print(priminess)
}
#Test with arbritary values
isprime(5)
isprime(6)
isprime(100000)
```

*You do not need to check all numbers from 2 to $x - 1$ to see if a number is prime. What is the largest you would need to go for an arbitrary $x$? Create a new function, `isprime2()`, that implements this better (yet still slow) method.*

```{r}
# Already done up there, the while loop exits if the value is found to be not prime.
```