---
title: "MATH 3070 Lab Project 1"
author: "Kanishka Ragula"
date: "August 24, 2017"
output:
  html_document:
    toc: TRUE
---

*Remember: I expect to see commentary either in the text, in the code with comments created using `#`, or (preferably) both! **Failing to do so may result in lost points!***

## Problem 1 (Verzani problem 1.1)
*Use R as you would a calculator to find numeric answers to the following:*

1. $1 + 2(3 + 4)$

```{r}
# Order of operations done.  The multiplication separates
# the parenthesis from the coefficient because it throws
# an error otherwise.
1 + 2 * (3+4)
```

2. $4^3 + 3^{2 + 1}$

```{r}
# Parenthesis are around the exponents
(4^3) + 3^(2+1)
```

## Problem 2 (Verzani problem 1.4)
*Use R to compute the following:*

$$\frac{0.25 - 0.2}{\sqrt{0.2(1-0.2)/100}}$$

```{r}
# Equation here
(.25-.2)/(sqrt(.2*(1-.2)/100))
```

## Problem 3 (Verzani problem 1.5)
*Assign the numbers 2 through 5 to different variables, then use the variables to multiply all the values.*

```{r}
# Assigning values to the variables
num_var2 = 2
num_var3 = 3
num_var4 = 4
num_var5 = 5
# Multiply all together
num_var2 * num_var3 * num_var4 * num_var5
```

