---
title: "MATH 3070 Lab Project 4"
author: "Kanishka Ragula"
date: "September 8, 2016"
output:
  html_document:
    toc: TRUE
---

*Remember: I expect to see commentary either in the text, in the code with comments created using `#`, or (preferably) both! **Failing to do so may result in lost points!***

## Problem 1 (Verzani problem 2.43)
*The `time` variable in the `nym.2002` data set (**UsingR**) contains the time to finish the 2002 New York City Marathon for a random sample of the finishers.*

1. *What percent ran the race in under 3 hours?*

```{r}
#Import library because we are obligated to
library(UsingR)


#Which creates a vector containing the desired values.
#Length tells us the amount in the vector
#Format the percent
paste(((length(which(nym.2002[5]<180))/nrow(nym.2002))*100), "%", sep="")

```

2. *Given that the slower runners will have higher running times; cut off the highest 10%.The highest 25%*

```{r}
#notTen stores the values of the marathon times not within the highest 10%
#Overkill, yeah...
notTen = nym.2002[which(nym.2002[5] < quantile(unlist(nym.2002[5]), .9)), 5]

#Desired answer apparently
quantile(unlist(nym.2002[5]), .9)

#not25 stores the values of the marathon times not within the highest 25%
#Overkill again...
notTen = nym.2002[which(nym.2002[5] < quantile(unlist(nym.2002[5]), .75)), 5]

#Why can't I just leave that?  Desired answer again
quantile(nym.2002$time, .75)
```

3. *Given that the faster runners will have lower running times, cut off the lowest 10%.*

```{r}
#notFast stores the times slower than the top 10% of runners (lowest time)
#Is Overkill needed anymore?
notFast = nym.2002[which(nym.2002[5] > quantile(unlist(nym.2002[5]), .9)), 5]

#Desired answer:
quantile(nym.2002$time, .1)
```

## Problem 2 (Verzani problem 4.1)
*The data set `UScereal` (**MASS**) contains data on cereals sold in the United States in 1993. For this data set, answer the following questions using R (i.e. MUST answer questions using a code. Do not count by hand):*

1. *How many rows does the data frame have? Columns?*

```{r}
#Number of rows
nrow(UScereal)

#Number of columns
ncol(UScereal)
```

2. *How many different manufacturers are included?*

```{r}
# Counts the number of levels in the manufacturers column
nlevels(UScereal$mfr)
```

3. *How many vitamin categories are included?*

```{r}
nlevels(UScereal$vitamins)

```

4. *How many cereals have a sugar level above 10?*

```{r}
#Count length of which vector for sugars above 10
length(which(UScereal$sugars>10))
```

5. *What is the mean calorie value for cereals with more than 5 grams of fat? Less than or equal to 5?*

```{r}
# Mean for more than 5
mean(UScereal[which(UScereal$fat>5), "calories"])

# Mean for less than 5
mean(UScereal[which(UScereal$fat<=5), "calories"])
```

6. *What is the mean calorie value for cereals on the middle shelf (2)?*

```{r}
# Returns mean calories for middle shelf cereals
mean(UScereal[which(UScereal$shelf == 2), "calories"])
```

## Problem 3
*Create a data frame containing the data in the following table:*

| First    | Last      | Age |
|----------|-----------|-----|
| Marcus   | Holstein  | 23  |
| Samuel   | Adams     | 56  |
| Gus      | McPherson | 43  |
| Margaret | Olsen     | 41  |
| Zim      | Newbold   | 95  |

```{r}
# Stores the First names, Last names, and Ages of people, each as its own vector stored in the data frame
df1 = data.frame(First = c("Marcus","Samuel","Gus","Margaret","Zim"), Last = c("Holstein","Adams","McPherson","Olsen","Newbold"), Age = c(23, 56, 43, 41, 95))
df1
```
