---
title: "MATH 3070 Lab Project 9"
author: "Kanishka Ragula"
date: "October 26, 2017"
output:
  html_document:
    toc: TRUE
---

*Remember: I expect to see commentary either in the text, in the code with comments created using `#`, or (preferably) both! **Failing to do so may result in lost points!***

## Problem 1 (Verzani problem 3.17)
*The `state.x77` data set contains various information for each of the fifty United States. We wish to explore possible relationships among the variables. First, we make the data set easier to work with by turning it into a data frame.*

```{r}
library(UsingR)
x77 <- data.frame(state.x77)

```

*Now, make scatter plots of `Population` and `Frost`; `Population` and `Murder`; `Population` and `Area`; and `Income` and `HS.Grad`. Do any relationships appear linear? Are there any surprising correlations?*

```{r, tidy=TRUE}
plot(Population ~ Frost, data = x77) #Plot the Pop data against Frost
cor(x77$Population, x77$Frost) #There is an R of -.33 so there is no useful correlation

plot(Population ~ Murder, data = x77) #Plots the population against murder
cor(x77$Population, x77$Murder) # There is a correlation of .34 so no useful correlation

plot(Population ~ Area, data = x77) # Plots the population against area
cor(x77$Population, x77$Area) # R of .02 so definitely no correlation

plot(Income ~ HS.Grad, data = x77) # Plots income against HS Grads
cor(x77$Income, x77$HS.Grad) # R of .62 so there is a slight linear correlation.
```

## Problem 2 (Verzani problem 3.20)
*The `batting` (**UsingR**) data set contains baseball statistics for the 2002 Major League Baseball season. What is the correlation between the number of strikeouts (`SO`) and the number of home runs (`HR`)? Make a scatter plot to see whether there is any trend. Does the data suggest that in order to hit a lot of home runs one should strike out a lot?*

```{r, tidy=TRUE}
cor(batting$SO, batting$HR) #Correlation method
plot(SO ~ HR, data = batting)
#It would appear there is a large correlation (.70) and trend between home runs and strikeouts.  This can be a Spurious Correlation as the number of strike outs doesn't impact homeruns.  Correlation doesn't equal causation.  In addition, these could be caused by the people who hit more home runs and strikeouts hitting more balls in general.
```

## Problem 3 (Verzani problem 3.32)
*The data set `UScereal` (**MASS**) contains information about cereals on a shelf of a United States grocery store. Make a table showing the relationship between manufacturer, `mfr`, and shelf placement, `shelf`. Are there any obvious differences between manufacturers?*

```{r, tidy=TRUE}
mfrShelf = xtabs(~mfr + shelf, data = UScereal)
ftable(mfrShelf)
#It would appear that Kellog, General Mills, and Post have large amounts of space on shelf 3.  Following this, General Mills, Quaker, and Kellog have shelf space on 2.  Finally, there is an even(ish) distribution on shelf 1 with Quaker not having any.
```

## Problem 4 (Verzani problem 3.33)
*The help page for `mosaicplot()` demonstrates the data set `HairEyeColor`, which records `sex`, `Hair` color, and `Eye` color for 592 statistics students. The data set comes as a flattened table, so simply passing the object to `mosaicplot()` will create the plot. (Or, as demonstrated, passing `shade = TRUE`, as in `mosaicplot(HairEyeColor, shade = TRUE)`, will produce a colored version.)*
*Make the plot. Why does the help page note, "there are more blue-eyed, blonde females than expected?"*

```{r, tidy=TRUE}
# Creates a plot of HairEyeColor and then makes it colorful
mosaicplot(HairEyeColor, shade = TRUE)
# When the shade is applied, the largest group is blond hair blue eyed females by a significantly large amount (very deep shade of blue).  This would suggest an uneven distribution of people in the class and blond haired blue eyed females really like statistics (not representative in the 3070 class)
```