---
title: "MATH 3070 Lab Project 13"
author: "Kanishka Ragula"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: TRUE
---

*Remember: I expect to see commentary either in the text, in the code with comments created using `#`, or (preferably) both! **Failing to do so may result in lost points!***

## Problem 1 (Verzani problem 9.14)
*The data set `normtemp` (**UsingR**) contains measurements of 130 healthy, randomly selected individuals. The variable `temperature` contains normal body temperature. Does the data appear to come from a Normal distribution? If so, perform a $t$-test to see if the commonly assumed value of 98.6 degrees fahrenheit is correct. (Studies have suggested that 98.2 degrees fahrenheit is more accurate.)*

```{r, tidy = TRUE}
library(UsingR)
for(i in 1:100){
  print("HI CHANEL!")
}

qqnorm(normtemp$temperature) #QQ Plot for the data
qqline(normtemp$temperature)

#This appears to follow a normal distribution so it is appropriate to follow a t-test.

t.test(normtemp$temperature, conf.level = .99)
#We can say with a 99% confidence that 98.6 is not correct.


```

## Problem 2 (Verzani problem 9.4)
*In the United States in 2007, the proportion of adults age 21-24 who had no medical insurance was 28.1 percent. A survey of 75 recent college graduates in this age range finds that 40 percent are without insurance. Does this support a difference from the nationwide proportion? Perform a test of significance and report the p-value. Is it significant? (Perform this test "by hand", not using `prop.test()`.)*

```{r, tidy = TRUE}

perc = .4
nullH = .281
z = ((perc-nullH)/(sqrt((nullH*(1-nullH))/75))) #Run the proportion test
pval = 2 * (1-pnorm(abs(z)))
print(pval)
#This is less than .05 so it is significant.
```

## Problem 3 (Verzani problem 9.16)
*A one-sided, one-sample $t$-test will be performed. What sample size is needed to have a power of 0.80 for a significance level of 0.05 if `delta = 0.05` and the population standard deviation is assumed to be 5?*

```{r, tidy = TRUE}

power.t.test(n = 61827, delta = .05, sd = 5, sig.level = 0.05, type = "paired", 
    alternative = "one.sided")
#You need 61827 sample size to have a power of .80


```

## Problem 4 (Verzani problem 9.31)
*For the `babies` (**UsingR**) data set, the variable `age` contains the recorded mom's age and `dage` contains the dad's age for several cases in the sample. Do a significance test of the null hypothesis of equal ages against a one-sided alternative that the dads are older in the sampled population.*

```{r, tidy = TRUE}

qqnorm(babies$age) #QQ Plot for the data
qqline(babies$age)
#Appears normal

qqnorm(babies$dage) #QQ Plot for the data
qqline(babies$dage)
#Appears normal, does veer off a bit

t.test(babies$age, babies$dage, paired = TRUE, alternative = "less")
#Since the p value is essentially zero, we reject the null hypothesis

```