---
title: "MATH 3070 Lab Project 2"
author: "Kanishka Ragula"
date: "August 31, 2017"
output:
  html_document:
    toc: TRUE
---

*Remember: I expect to see commentary either in the text, in the code with comments created using `#`, or (preferably) both! **Failing to do so may result in lost points!***

## Problem 1 (Verzani problem 1.7)
*The `exec.pay` (**UsingR**) data set is available after loading the package **UsingR**. Load the package, and inspect the data set. Scan the values to find the largest one.*

```{r}
require(UsingR) #Large amont of console data comes out
data(exec.pay) # Use the data set
max(exec.pay) # Find the max
```

## Problem 2 (Verzani problem 2.4)
*Create the following sequences, using `:`, `seq()`, or `rep()` as appropriate:*

1. `"a" "a" "a" "a" "a" "a"`

```{r}
rep("a", each = 6) #Repeats a 5 times
```

2. `1 3 ... 99` *(the odd numbers)*

```{r}
seq(1,99,by=2) # Sequence from 1 to 99 going by every 2
```

3. `1 1 1 2 2 2 3 3 3`

```{r}
rep(c(1, 2, 3), each=3) #Repeats every element in vector 3 times
```

## Problem 3 (Verzani problem 2.3)
*Let our small data set be* `2 5 4 10 8`.

1. *Enter this data into a data vector `x`.*

```{r}
x = c(2,5,4,10,8) #Stores desired values in x
```

2. *Find the square of each number.*

```{r}
x^2 #Squares every value in x
```

3. *Subtract 6 from each number.*

```{r}
x-6 # Subtracts 6 from every element in x
```

4. *Subtract 9 from each number and then square the answer.*

```{r}
(x-9)^2 #First subtracts 9 within the parenthesis and then squares
```