---
title: "MATH 3070 Lab Project 8"
author: "Kanishka Ragula"
date: "October 19, 2017"
output:
  html_document:
    toc: yes
  pdf_document:
    toc: yes
---

*Remember: I expect to see commentary either in the text, in the code with comments created using `#`, or (preferably) both! **Failing to do so may result in lost points!***

## Problem 1 (Verzani problem 3.2)
*For the `michelson` (**MASS**) data set, produce a density plot comparing `Speed` between Experiments 1 and 2.*

```{r, tidy=TRUE, error=TRUE}
#Library stuffs
library(UsingR)
library(aplpack)
#Split the data by experiment
mich_split = with(michelson, split(Speed, Expt))

#Create vectors for each experiment
exp1 = mich_split$"1" 
exp2 = mich_split$"2"

#Plot the data after giving the title
plotOne = plot(density(exp2),main = "Density Plot of Michelson Experiments 1 and 2 (Exp1 is dotted)", lty = 1)
lines(density(exp1), lty = 2)

```

## Problem 2 (Verzani problem 3.4)
*Three students record the time spent on homework per class. Their data is:*

| Student| 1  | 2  | 3  | 4  | 5 |
|:-------|---:|---:|---:|---:|--:|
| Marsha | 25 | 0  | 45 | 90 | 0 |
| Bill   | 30 | 30 | 30 | 30 |   |
| Holly  | 15 | 0  | 90 | 0  |   |

*Use a list to store these values. Then create a boxplot to compare. (You must use `boxplot()`'s formula interface for this problem.)*

```{r, tidy=TRUE, error=TRUE}
library(Hmisc)
#Library Stuffs again
#Create the data lists by person and class
Class = c(1,2,3,4,5)
Marsha = c(25, 0, 45, 90, 0)
Bill = c(30,30,30,30, 0)
Holly = c(15, 0, 90,0, 0)

#Create a data frame to store this
y=data.frame(Class, Marsha, Bill, Holly)
boxplot(t(y))
#Plot the transpose of the boxplot to compare classes

```

## Problem 3 (Verzani problem 3.5)
*A group of nursing students take turns measuring some basic assessments. Their data is:*

|          | Temp | Pulse | Systolic | Diastolic |
|----------|------|-------|----------|-----------|
| Jackie   | 98.2 | 96    |  134     | 90        |
| Florence | 98.6 | 56    |  120     | 80        |
| Mildred  | 98.2 | 76    |  150     | 95        |

*Create a data frame of these values. Will `plot()` and `boxplot()` produce the same graphic?*

```{r, tidy=TRUE, error=TRUE}
#Create the data vectors for each type of data
Name = c("Jackie", "Florence", "Mildred")
Temp = c(98.2, 98.6, 98.2)
Pulse = c(96,56,76)
Systolic = c(134, 120, 150)
Diastolic = c(90,80,95)

#Create the data frame
x = data.frame(Name, Temp, Pulse, Systolic, Diastolic)
#Plot the data
plot(x)
boxplot(x[2:5])

#These give different results
```

## Problem 4 (Verzani problem 3.8)
*The second argument to `split` can be a list of factors. The result is that all interactions (possible combinations) are used for the groups. In the `ToothGrowth` data set, growth (`len`) is measured for two types of supplements (`supp`) and three doses (`dose`). Split this `len` value into 6 groups.*

```{r, tidy=TRUE, error=TRUE}
split(ToothGrowth$len, paste(ToothGrowth$supp, ToothGrowth$dose)) #Breaks len by the Supplement and Dose
```